---
title: "ML"
description: |
  This exercise shows off how Machine Learning is used. 
date: "`r Sys.Date()`"
output: distill::distill_article
---

##  Dimensionality Reduction 

- Explanation
Using this machine learning technique can help you cut down on the different dimensions that must be processed.  This technique brings out relationships between the original dimensions to identify new dimensions that better capture the relationships within the data.


- Process and Results
The graph show that PC1 and PC 2 had the most variances. 

- How it applies to Accounting
It can help identify the most important features for a data set which will cut down the work that the accountant has to do.


```{r}
library(caret)
#store our data in another object
dat <- iris
#take the 4 continuous variables and perform PCA
caret.pca <- preProcess(dat[,-5], method="pca",pcaComp=2)

caret.pca
```
```{r}
caret.pca$
#use that data to form our new inputs
dat2 <- predict(caret.pca, dat[,-5])


#using stats
stat.pca <- prcomp(dat[,-5],
                 center = TRUE,
                 scale. = TRUE) 

# plot method
plot(stat.pca, type = "l")
```

```{r}
summary(stat.pca)
```

